How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-01 tse-paper/content.tex
Add content
Small fix
Add new motivating section

% TODO Caro: I moved it to the intro
% --- please check how it works for you
Retrospectively analyzing the build logs is not the only solution to
the problem---an alternate would be to integrate live plugins into the
build process
 such as the JUnit
plugin for Jenkins~\cite{jenkins2020junit-plugin} or
Deflaker by Bell et al.~\cite{bell2018deflaker}.

@@

% ----- descriptive / general -----
Our literature survey shows that despite its relatively young age
(first mentioned in a paper in 2001, vast majority after
2016), \emph{build log analysis is already an established technique,}
with 61 works in different venues making use of it for a variety of
purposes.
We saw that various researchers analyze build logs, often because the
logs are the only available source for the
information they need for their studies~\cite{ren2018automated,
seo2014programmers,beller2017oops,zampetti2017open,rausch2017empirical}.

% ----- information RQ 1.1 -----
In regards to the information that is targeted, \emph{most build log
analysis approaches aim to retrieve the reason a build failed} by
targeting ``errors'' or ``failing tests.''
% which is what we also do in LogChunks
\emph{The majority of approaches retrieves specific chunks of
text from the logs.} Chunks in some sense are the overarching concept to
the almost equally used categorization, as a categorization can usually
be deducted from chunks, but not vice versa.

@@

% ----- kinds of build logs RQ1.3 -----
Several works noted the variety in log formats for different build
tools, which requires customizing build log techniques for
every supported build tool.
\Cref{fig:litsur:log_producer} shows that there are only a handful of
build tools whose build logs more than one study analyzed, mainly in
the Java ecosystem (area \circlenum{A}).
Many works target a unique build tool that did not appear in any other
study (area \circlenum{B}).

\emph{seldomly-investigated
environments would benefit from the
existence of a more generic solution.}
% In most cases, \emph{researchers analyze build logs from open
% source projects}, obtained through Travis CI.
% In addition, we saw several works that targeted the logs of only
% one specific software project.

@@

% TODO Moritz: is this okay (here)?
% maybe it's better to add it to Threats to Validity with the heading:
% \texbf{Modifying the Build Process.}
% Moritz: I think best to decided once we read the paper
% top to bottom.
%For now, it seems ok
% Needs to go Threats or intro

@@

In summary, the outcome of the literature survey shows the need for
build log
analysis techniques that are \emph{automated},
\emph{build tool-agnostic}
and can be \emph{configured with little effort}.

To address this need,
we propose a set of so called \emph{chunk retrieval techniques},
which retrieve a specific substring (called chunk)
from a build log.
The techniques we propose run automatically
and can be easily configured through examples.
An example in this case consists of a build log together with the
chunk that should be retrieved.
A user---a developer or a researcher who wants to analyze
build logs---provides these examples, which are easy to
adapt whenever the analysis technique needs
to support new cases.

We designed and implemented three chunk retrieval
techniques based on approaches
previously described by several works:
\emph{Program Synthesis by Example (PBE)}
mimics regular expressions, while simplifying
their development.
From the field of information retrieval, we leverage a
\emph{Common Text Similarity (CTS)} approach
and implement the ad hoc approach of
searching for specific strings as \emph{Keyword Search (KWS)}.

In this section, we define our concept of chunk
retrieval techniques and present each of the techniques
we developed in detail.
Following that, we illustrate how the techniques
operate on a concrete
example and sketch out their implementation.

\begin{table*}[htb]
\centering
\caption{Chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}llXll@{}}
\toprule
Name			     & Acronym & Identification Technique
& Granularity & Configuration \\
\midrule
Program Synthesis by Example & PBE     & Regular expression program
& Character   & In/output examples	\\
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
\bottomrule
\end{tabularx}
\label{tab:techniques}
\end{table*}

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:crt-characteristics}
Before introducing each of the techniques, we formalize
we formalize our concept of chunk retrieval techniques.
By this phrase, we refer to techniques that automatically
retrieve pieces of information that appear literally in build
logs, i.e., techniques that do not aggregate, combine, or deduct
information.
We call such pieces of information in build logs
\emph{chunks}.

Generally, chunk retrieval techniques
can also be used to classify build logs, e.g.\ by checking
which substring was retrieved.
Therefore, they
cover the great majority of the types of log analysis we saw within
our survey.

@@

\emph{Running a
chunk retrieval technique} means applying a fully configured
technique to a build log in plain text format.
The technique then outputs a list that consists of substrings of the
build log text.
In \Cref{tab:techniques}, we summarize and distinguish the techniques
we present along the characteristics described above.

@@

For each build log, we manually marked
the chunk that describes why the build
failed---the information targeted by most of the works in our
literature survey.
To be able to configure the keyword search technique,
the data set associates each chunk with keywords that we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.

>>>>

% TODO Moritz: is this okay (here)?
% maybe it's better to add it to Threats to Validity with the heading:
% \texbf{Modifying the Build Process.}
% Moritz: I think best to decided once we read the paper
% top to bottom.
%For now, it seems ok
% Needs to go Threats or intro
% TODO Caro: I moved it to the intro
% --- please check how it works for you
Retrospectively analyzing the build logs is not the only solution to
the problem---an alternate would be to integrate live plugins into the
build process
 such as the JUnit
plugin for Jenkins~\cite{jenkins2020junit-plugin} or
Deflaker by Bell et al.~\cite{bell2018deflaker}.

@@

% ----- descriptive / general -----
Our literature survey shows that despite its relatively young age
(first mentioned in a paper in 2001, vast majority after
2016), \emph{build log analysis is already an established technique,}
with 61 works in different venues making use of it for a variety of
purposes.
We saw that various researchers analyze build logs, with the
logs often being the only available source for the
information they need for their studies~\cite{ren2018automated,
seo2014programmers,beller2017oops,zampetti2017open,rausch2017empirical}.

% ----- information RQ 1.1 -----
In regards to the information that is targeted, \emph{most build log
analysis approaches aim to retrieve the reason a build failed} by
targeting ``errors'' or ``failing tests.'' 
% which is what we also do in LogChunks
\emph{The majority of approaches retrieves specific chunks of
text from the logs.} Chunks are the overarching concept to
the almost equally much used categorization: one can deduce a categorization from chunks, but not vice versa.

@@

% ----- kinds of build logs RQ1.3 -----
Several works noted the variety in log formats for different build
tools, which requires customizing build log techniques for
every supported build tool.
\Cref{fig:litsur:log_producer} shows that there are only a handful of
build tools whose build logs more than one study analyzed, mainly in
the Java ecosystem (area \circlenum{A}).
Many works target a unique build tool that did not appear in any other
study (area \circlenum{B}).
We follow that \emph{many seldomly-investigated
environments would benefit from the
existence of a more generic solution.}

% TODO passive ...
The literature survey shows the need for
build log
analysis techniques that are \emph{automated},
\emph{build tool-agnostic}
and can be \emph{configured with little effort}.

% In most cases, \emph{researchers analyze build logs from open
% source projects}, obtained through Travis CI.
% In addition, we saw several works that targeted the logs of only
% one specific software project.

@@

@@

% TODO This introduction is weird
In this section, we formally define the concept of chunk
retrievals from build logs. Then, we motivate and present the choice of three such techqniues that we implemented for this study in detail.

In this section,
we propose three so-called \emph{chunk retrieval techniques},
which retrieve a specific substring (chunk)
from a build log
% TODO passive ....
The techniques we propose run automatically
and can be easily configured through examples.
% TODO this should go under characteristics and not be in an introduction to the section ...
An example in this case consists of a build log together with the
chunk that should be retrieved.
A user---a developer or a researcher who wants to analyze
build logs---provides these examples, which are easy to
adapt whenever the analysis technique needs
to support new cases.

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:crt-characteristics}
% TODO (resolved) Never define a concept with the
% words used in the term
% Use a thesaurus to find synonyms

With the term ``chunk retrieval technique,'' we refer to a way of automatically extracting strings that appear literally in build
logs, i.e., techniques that do not aggregate, combine, or deduct
information.
We call such pieces of information in build logs
\emph{chunks}.

Generally, chunk retrieval techniques
can also be used to classify build logs, e.g.\, by checking
which substring was retrieved.
Therefore, they
cover the great majority of the types of log analysis we saw in \Cref{sec:lit-sur:discussion}.

@@

\emph{Running a
chunk retrieval technique} means applying a fully configured
technique to a build log in plain text format.
The technique then outputs a list that consists of substrings of the
build log text.

\subsection{Choice of Chunk Retrieval Techniques}
For this article, we designed and implemented three automated chunk
retrieval techniques. The strategies that underlie them were inspired
based on techniques we found in the literature survey and other
research fields. 
In \Cref{tab:techniques}, we summarize and distinguish the techniques
we present along the characteristics described above.

Techniques based on custom parsers (\#1
in \Cref{tab:litsur:techniques}) are inadquate for our comparison,
since their creation is manual and such a technique would not
generalize on the wide varitey of build logs we are interested in. The
closest we could come to the second entry, regular expression, is a
technique to automatically derive them: In particular, we implement a
technique based on
\emph{Program Synthesis by Example (PBE)}. This 
mimics regular expressions, the second most frequently occurring whose while simplifying
their development.

To work effectively with build logs, many humans anecdotally search
(``grep'') the logs for key phrases such as ``fail.'' Papers often
resorted to such a strategy when doing manual analysis (\#2
in \Cref{tab:litsur:techniques}), describing it with the word
``scan.'' Imitating this ad hoc approach of searching for specific
strings, we automatize it as \emph{Keyword Search (KWS)}.

Finally, from the fields of information retrieval and natural language
processing, we leverage a
\emph{Common Text Similarity (CTS)} approach. The reason for it is that the relevant, failing parts of build logs often looks similar to each other, even if the exact failure reason might differ.

\begin{table*}[htb]
\centering
\caption{Chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}llXll@{}}
\toprule
Name & Acronym & Identification Technique & Granularity &
Configuration \\
\midrule
Program Synthesis by Example & PBE     & Regular expression program
& Character   & In/output examples	\\
% TODO: TF-IDF still not defined
Common Text Similarity	     & CTS     & TF-IDF \& cosine similarity,
expected number of lines & Line        & Output examples	   \\
Keyword Search		     & KWS     & Keywords, expected number of
lines			 & Line        & Keywords, context length  \\
Random Line Retrieval	     & RLR     & Random sample
& Line	      & Retrieval length	  \\
\bottomrule
\end{tabularx}
\label{tab:techniques}
\end{table*}

@@

For each build log, we manually marked
the chunk that describes why the build
% TODO add back ref
failed---the information targeted by most of the works in our
literature survey.
To be able to configure the keyword search technique,
the data set associates each chunk with keywords that we
would use to search for the selected chunk within the log.
In
addition, we categorized the log chunks according to their format
within the log.
If the chunks were surrounded by the same markings
within the log, we assigned them the \emph{same structural category},
as described in \Cref{sec:crt-example}.
